InformatiCup 2024 Ctrl-Alt-Defeat

### 2024-01-14 paper.tex
Added citation

\subsubsection{Image generating models}
The first image generative model we use is the Stable Diffusion model. It is developed by engineers and researchers from CompVis (\url{https://github.com/CompVis}), Stability AI (\url{https://stability.ai/}) and LAION (\url{https://laion.ai/}) \cite{patil2022stable}.

Diffusion models achieve state-of-the-art synthesis results on image data by decomposing the image formation process into sequential applications of denoising autoencoders. Due to its work directly in pixel space, they are very computational expensive. To lower the computational costs, the Stable Diffusion model is applied in a latent space of powerful pretrained autoencoders. This works without losing quality and flexibility. \cite{Rombach_2022_CVPR}

\subsubsection{Text generating models}

>>>>

\subsubsection{Image generating models}

\subsubsection{Text generating models}
We choose the GPT model as one possibility to generate texts for testing our augmentation methods. The GPT model tries to counter the scarcity of labeled text data for machine learning.

\cite{radford2018improving} try to avoid this problem in a simple two step procedure:
\begin{enumerate}
	\item A generative pre-training of a language model on a varying corpus of unlabeled text.
	\item Discriminative fine-tuning on every specific task.
\end{enumerate}

To achieve effective transfer with minor changes to the model architecture, task-aware input is used during transformations. \cite{radford2018improving}
